{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed Object Tracking

### 2017-11-27 wacv_for_review.tex
References updated with ECO, CCOT and SCT

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical
applications running on embedded systems. This is primarily because
most of embedded systems come with an image acquisition pipeline, and
a tremendous amount of progresses on computer vision research has been
made for the past few decades. However, to successfully deploy a
computer vision algorithm on any existing embedded systems, a vision
algorithm needs to satisfy, at least, two criteria with the assumption
of reasonably good performance: minimal, manual intervention after
deployment and small footprint of consuming computational
resources. Kept these criteria in mind, to develop a single, target
tracking system, we propose an ensemble of the kernelized correlation
filters (KCF), we call {\it E}nKCF. This committee of KCFs is
specifically designed to address the scale-change and dynamic maneuver
of the target over frames. In particular, to guarantee a high-speed,
run-time performance, we deploy each of KCFs in turn, instead of
applying multiple KCFs on each frame. To minimize any potential drifts
between individual KCFs' transition, we developed a Bayes
filter. Experimental results showed that the performance of ours are,
on average, 70.10\% for precision at 20 pixels, 53.00\% for success
rate for OTB100 data, and 54.50\% and 40.2\% for UAV123 data. These
results showed that our method is better than existing ones over 5\%
on precision on 20 pixels and 10-20\% on AUC on average. Moreover our
implementation ran at 340 fps for OTB100 and at 416 fps for UAV123
data that is faster than DCF (292 fps) for OTB100 and KCF (292 fps),
DCF (457 fps) for UAV123. To increase flexibility of the proposed {\it
  E}nKCF running on various single-board computers, particularly, ones
with GPUs, we explored different levels of deep features.
\end{abstract}

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical
applications running on embedded systems. This is primarily because
most of embedded systems come with an image acquisition pipeline, and
a tremendous amount of progresses on computer vision research has been
made for the past few decades. However, to successfully deploy a
computer vision algorithm on any existing embedded system, a vision
algorithm needs to satisfy, at least, two criteria with the assumption
of reasonably good performance: minimal, manual intervention after
deployment and small footprint of consuming computational
resources. Keeping these criterias in mind, we propose an ensemble of the 
kernelized correlation filters (KCF), called {\it E}nKCF, to develop a single target
tracking system. This committee of KCFs is
specifically designed to address the scale-change and dynamic maneuver
of the target over frames. In particular, to guarantee a high-speed
run-time performance, we deploy each of KCFs in turn, instead of
applying multiple KCFs on each frame. To minimize any potential drifts
between individual KCFs' transition, we developed a Bayes
filter. Experimental results showed that the performance of ours are,
on average, 70.10\% for precision at 20 pixels, 53.00\% for success
rate for OTB100 data, and 54.50\% and 40.2\% for UAV123 data. These
results showed that our method is better than other high-speed trackers over 5\%
on precision on 20 pixels and 10-20\% on AUC on average. Moreover, our
implementation ran at 340 fps for OTB100 and at 416 fps for UAV123
dataset that is faster than DCF (292 fps) for OTB100 and KCF (292 fps) 
for UAV123. To increase flexibility of the proposed {\it E}nKCF running on 
various single-board computers, particularly ones
with GPUs, we explored different levels of deep convolutional features.
\end{abstract}
